### 2018-09-20 FrascatiPlot/Paper/aps/main.tex
for journal submission: yet another minor revision to the text of difference between data and models - it can be shortened more perhaps

In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining Eq.~\ref{eq:BA_general} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:

@@

\subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to both coalescence and thermal model predictions. For the coalescence predictions, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}. The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}.

As a first observation, one sees that for deuterons both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 1.5 to 2. The limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data. 
Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree. 
As a matter of fact, the only data point available so far in Pb--Pb collisions is in agreement with the thermal+blast-wave model but not with coalescence. The difference between data and the coalescence model is about 6$\sigma$. However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production. This is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}. According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.

>>>>

In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see details in next section) and by combining %Eq.~\ref{eq:BA_general} 
Eq. 6.2 in \cite{Scheibl:1998tk} and Eq.~\ref{eq:CA_general}, we obtain the following general expression for the coalescence parameter:

@@

\subsection{Thermal and coalescence model for $\mathbf{A = 2, 3}$ anti- and hyper-nuclei}
In Fig.~\ref{fig:CompareThermalAndCoalescence}, the available data for (anti-)deuterons, (anti-)\hethree\ and (anti-)\hthreelambda~\cite{Adam:2015yta} are compared to coalescence and to the thermal model+blast wave predictions described in Sec.~\ref{sec:thermal}.
%both coalescence and thermal model predictions. 
%For the coalescence predictions, 
For the latter and for data, the radius parameterisation B is used, as discussed in Sec.~\ref{sec:radiiParamet}. 
%The combined thermal model and blast-wave predictions are calculated as described in Sec.~\ref{sec:thermal}. 
%As a first observation, one sees that

For deuterons, both approaches lead to similar predictions and give a reasonable description of the experimental data for $R \gtrsim 1.6$ fm. 
For \hethree~the two models exhibit a qualitatively similar trend as a function of $R$, but they differ by a factor of about 1.5 to 2. The limited amount of data that is currently available is consistent with both models within 2$\sigma$ to 3$\sigma$, where $\sigma$ is the total uncertainty on the data. 
Both approaches show large differences (a factor 5 to 6 for central Pb--Pb collisions and a factor larger than 50 for small radii, $R < 2$ fm) for the \hthreelambda\ caused by the significantly larger size of \hthreelambda\ with respect to \hethree. 
%As a matter of fact, 
The only data point available so far in Pb--Pb collisions is in agreement with the thermal model but not with coalescence. 
The difference between data and the coalescence model is about 6$\sigma$,
%However, it is to be kept in mind that the considerations expressed here are subject to the validity of our assumptions, \textit{in primis} the usage of a gaussian form for the wave-function.
albeit the validity of our assumptions (\textit{in primis} the usage of a gaussian wave-function).
%
%Some authors argue that the difference of data to the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons~\cite{Zhang:2018euf}. 
%In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production. This is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}. According to our understanding, in both the coalescence and the thermal model calculations the presence of excited states enters via a spin degeneracy factor $(2J_{A}+1)$ and thus the predictions would increase by the same factor.
%
In \cite{Zhang:2018euf} it is argued that the difference between data and the coalescence model might be explained by a later formation through the coalescence of $\Lambda$s and deuterons. 
A possible difference attributable to the presence of excited states with $J=3/2$ of \hthreelambda, which would significantly enhance the phase space for its production, is not considered here as there is no evidence for the existence of such an excited state~\cite{Mart:1996ay}.
